Supplementary

### 2021-11-17 manuscript.Rmd
*tab 1

```{r}
relevant.scale.data <- readxl::read_excel("Table_raw/relevant_scales.xlsx")
```

```{r results='asis'}
relevant.scale.data %>%
   kable( booktabs = T, caption ="Releated Scales", format ="latex", longtable =T) %>% 
  kable_styling(latex_options = c("repeat_header")) %>% 
  column_spec(1:6, width = "2cm")
```

>>>>

```{r relscale, include=F, warning=F, message=F}
relevant.scale.data <- readxl::read_excel("Table_raw/relevant_scales.xlsx")
```

```{r scalePrint, results='asis'}
relevant.scale.data %>%
   kable( booktabs = T, caption ="Releated Scales", format ="latex", longtable =T) %>% 
  kable_styling(latex_options = c("repeat_header")) %>% 
  column_spec(1:6, width = "2cm")
```
